Neighbor-Based Decentralized Training Strategies for Multi-Agent Reinforcement Learning

### 2024-10-03 paper-2024-sac-marl-neighbouring-strategies.tex
chore: massage on abstract

\begin{abstract}
Multi-agent deep reinforcement learning (MADRL) is gaining popularity as a powerful extension of
  single-agent reinforcement learning for training collaborative or competitive agents
  in complex environments. 
%
MADRL, however, introduces unique challenges, such as non-stationarity, partial observability, 
  and credit assignment that complicate the learning process.
%
Typically, in the literature, centralized training methods are used to tackle some of these challenges, 
  although they often face scalability limitations as the number of agents grows.
%
For this reason, decentralized training techniques have been proposed, however, 
  generally they have a longer convergence time compared to centralized ones 
  and may lead to instability.
%
This paper investigates the effectiveness of various neighbor-based decentralized training strategies based 
  on the well-known Deep-Q Learning algorithm as a viable alternative to centralized training. 
%  
We evaluate experience sharing, nearest neighboring averaging, and nearest neighboring consensus methods 
  in a custom multi-agent environment and compare their performance against centralized training
  and totally decentralized training. 
%  
Our results show that neighbor-based methods can achieve comparable performance to centralized training 
  while offering improved scalability and communication efficiency. 
%
% Finally, we discuss the trade-offs between these methods and provide insights into their applicability 
%   in different scenarios.
\end{abstract}

>>>>

\begin{abstract}
Multi-agent deep reinforcement learning (MADRL) is rapidly emerging as a powerful extension of single-agent reinforcement learning, 
enabling the training of both collaborative and competitive agents in complex environments. 
%
The most widely adopted training paradigm in MADRL is centralized training with decentralized execution (CTDE), which has demonstrated significant effectiveness. 
%
However, it relies on a centralized learner, requiring agents to learn in an offline setting and execute online. To address this limitation, decentralized training methods have been introduced. 
%
While these techniques offer greater flexibility, they tend to have slower convergence and can suffer from instability compared to centralized approaches.
%
This paper investigates the effectiveness of various neighbor-based decentralized training strategies based 
  on the well-known Deep-Q Learning algorithm as a viable alternative to centralized training. 
%  
We evaluate experience sharing, nearest neighboring averaging, and nearest neighboring consensus methods 
  in a custom multi-agent environment and compare their performance against centralized training
  and totally decentralized training. 
%  
Our results show that neighbor-based methods can achieve comparable performance to centralized training 
  while offering improved scalability and communication efficiency. 
%
% Finally, we discuss the trade-offs between these methods and provide insights into their applicability 
%   in different scenarios.
\end{abstract}
